Assessing primitives performance\\ on multi-stage execution

### 2018-05-06 paper.tex
first try at box plotting. add the bench raw data

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{ifthen}
%\input{macros.tex}

@@

\paragraph{Baseline: pure Smalltalk.}
: baseline
Smalltalk code on top of VM. Used as our baseline for benchmarks.
Write down the Smalltalk code here.
Expliquer to:do: over do: (to explain expresiveness) => core lib often use to:do: and not do:

@@

\paragraph{Existing: Smart Syntax Plugin.}
%CHECK how to import code env in latex.
%Note we're talking about comparison, not =, so not sure we should show = or bench =
%\begin{code}
%= aString 	
%	self == aString ifTrue: [ ^true ].
%	aString isString ifFalse: [ ^false ].
%	self size = aString size ifFalse: [ ^false ].
%	1 to: self size do: [:i | (self at: i) = (aString at: i) ifFalse: [ ^ false ] ].
%	^ true
%\end{code}
Restricted Smalltalk

@@

>>>>

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{ifthen}
\usepackage{pgfplots}
\usepgfplotslibrary{statistics}
%\input{macros.tex}

@@

\paragraph{Baseline: pure Smalltalk.}
: baseline
Smalltalk code on top of VM. Used as our baseline for benchmarks.
Write down the Smalltalk code here.
%CHECK how to import code env in latex.
%Note we're talking about comparison, not =, so not sure we should show = or bench =
%\begin{code}
%= aString 	
%	self == aString ifTrue: [ ^true ].
%	aString isString ifFalse: [ ^false ].
%	self size = aString size ifFalse: [ ^false ].
%	1 to: self size do: [:i | (self at: i) = (aString at: i) ifFalse: [ ^ false ] ].
%	^ true
%\end{code}
Expliquer to:do: over do: (to explain expresiveness) => core lib often use to:do: and not do:

@@

\paragraph{Existing: Smart Syntax Plugin.}
Restricted Smalltalk

@@

taille 0

\begin{tikzpicture}
  \begin{axis}
  [
boxplot/draw direction
=y,
    xtick={1,2,3},
    xticklabels={Plugin, Slang, Slang+JIT},
    ]
    \addplot+[
    boxplot prepared={
      median=2.942,
      upper quartile=2.977,
      lower quartile=2.911,
      upper whisker=3.098,
      lower whisker=2.797
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.9594,
      upper quartile=0.9791,
      lower quartile=0.9230,
      upper whisker=1.1059,
      lower whisker=0.8705
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.4258,
      upper quartile=0.4310,
      lower quartile=0.4227,
      upper whisker=0.5181,
      lower whisker=0.4074
    },
    ] coordinates {};
  \end{axis}
\end{tikzpicture}

taille 5

\begin{tikzpicture}
  \begin{axis}
  [
boxplot/draw direction=y,
    xtick={1,2,3},
    xticklabels={Plugin, Slang, Slang+JIT},
    ]
    \addplot+[
    boxplot prepared={
      median=0.6904,
      upper quartile=0.6998,
      lower quartile=0.6835,
      upper whisker=0.7353,
      lower whisker=0.6407
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.2530,
      upper quartile=0.2594,
      lower quartile=0.2449,
      upper whisker=0.2836,
      lower whisker=0.2323
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.1455,
      upper quartile=0.1475,
      lower quartile=0.1425,
      upper whisker=0.1636,
      lower whisker=0.1266
    },
    ] coordinates {};
  \end{axis}
\end{tikzpicture}

taille 100
\begin{tikzpicture}
  \begin{axis}
  [
boxplot/draw direction=y,
    xtick={1,2,3},
    xticklabels={Plugin, Slang, Slang+JIT},
    ]
    \addplot+[
    boxplot prepared={
      median=0.10378,
      upper quartile=0.10435,
      lower quartile=0.10355,
      upper whisker=0.10586,
      lower whisker=0.09964
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.05689,
      upper quartile=0.05706,
      lower quartile=0.05648,
      upper whisker=0.05985,
      lower whisker=0.05527
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.05564,
      upper quartile=0.05560,
      lower quartile=0.05552,
      upper whisker=0.05985,
      lower whisker=0.05382
    },
    ] coordinates {};
  \end{axis}
\end{tikzpicture}

taille 10000
\begin{tikzpicture}
  \begin{axis}
  [
boxplot/draw direction
=y,
    xtick={1,2,3, 4},
    xticklabels={Baseline, Plugin, Slang, Slang+JIT},
    ]
    \addplot+[
    boxplot prepared={
      median=10474,
      upper quartile=10506,
      lower quartile=10455,
      upper whisker=11905,
      lower whisker=10099
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=761,
      upper quartile=761,
      lower quartile=761,
      upper whisker=765,
      lower whisker=760
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=476.7,
      upper quartile=477,
      lower quartile=476,
      upper whisker=482,
      lower whisker=475
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=500,
      upper quartile=501.8,
      lower quartile=500,
      upper whisker=512,
      lower whisker=499
    },
    ] coordinates {};
  \end{axis}
\end{tikzpicture}
